\documentclass[10pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\begin{document}
CSE 015 Homework 2
Veronika Nechaeva \\[\baselineskip] 
Logical Identities 

1. $\neg$(p $\rightarrow$ (q $\rightarrow$ p))

Step 1: p $\land$ $\neg$(q $\rightarrow$ p) 
(Since $\neg$(p $\rightarrow$ q) $\equiv$ p $\land$ $\neg$ q)

Step 2: p $\land$ q $\land$ $\neg$ p
(Since $\neg$(p $\rightarrow$ q) $\equiv$ p $\land$ $\neg$ q)

Step 3: p $\land$ $\neg$ p
(Since p $\land$ $\neg$ p will always equal false, 

q has no influence on the identity)
\\[\baselineskip] 
2. $\neg$ ((p $\land$ q) $\rightarrow$ (q $\lor$ p))

Step 1: (p $\land$ q) $\land$ $\neg$(q $\lor$ p)
(Since $\neg$(p $\rightarrow$ q) $\equiv$ p $\land$ $\neg$ q)

Step 2: p $\land$ q $\land$ $\neg$ q $\land$ $\neg$ p
(De Morgan's law. This expression 

will always evaluate to false since it has p 
and $\neg$ p and q and $\neg$ q)
\\[\baselineskip] 
Logical Consequence 

1. Jimmy is smart, smart people are rich, therefore, Jimmy is rich. 

This inference is valid since it states that all smart people are rich, 

therefore Jimmy must be rich because he is smart.

2. Islands are surrounded by water, Puerto Rico is surrounded by water, 

therefore, Puerto Rico is an island. 

This inference is not valid. It was stated that all islands are surrounded 

by water,but it did not say whether all lands surrounded by water are 

islands or not. So just knowing that Puerto Rico is surrounded by water is

not enough to conclude that Puerto Rico is indeed an island based on the 

claims made.
\\[\baselineskip] 
Translating English Sentances into Formulas 

1. Not every student in CSE015 plays a musical instrument 
Translation: $\forall$ x $\neg$(S(x) $\rightarrow$ M(x))

2. A person is either a CSE015 student or plays a musical instrument, 

but not both.
Translation: $\forall$ x (S(x) $\lor$ M(x)) $\land$ $\neg$(S(x) $\land$ M(x))

3. There exists at least one student in CSE015 who does not play musical 

instrument.

Translation: $\exists$ x (S(x) $\land$ $\neg$M(x))
\\[\baselineskip] 
Logical equivalence

$\forall$x(A(x) $\land$ B(x)) $\equiv$ $\forall$x(A(x) $\rightarrow$ B(x))

\begin{displaymath}
\begin{array}{|c c|c|c|}
A(x) & B(x) & A(x) \land B(x) & A(x) \rightarrow B(x)\\
\hline
T & T & T & T\\
T & F & F & F\\
F & T & F & T\\
F & F & F & T\\
\end{array}
\end{displaymath}

As we can see by the truth table, this logical equivalence is not valid.



\end{document}