 \documentclass[10pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\begin{document}
Name: Veronika Nechaeva

Homework - 01

Knowledge Representation.\\[\baselineskip]  Problem 1.

1. It is not cloudy and it is not raining. Solution: Let p = it is cloudy, 

and let q = it is raining. 
Then $\neg$p $\land$ $\neg$q .

2.  I like to eat apples and bananas. Solution: Let p = I like to eat 

   apples, 
and let q = I like to eat bananas. Then p $\land$ q .

OR

Solution: Let p = I like to eat apples, and let q = bananas. 
Then p $\land$ q .

3. Behind the clouds the sun is shining. Solution: Let p = behind 

   the clouds, 
and let q = the sun is shining. Then p $\rightarrow$ q .

4. If a function is differentiable then the function is continuous.

Solution: Let p = the function is differentiable,
and let q = the function is 

continuous.
Then p $\rightarrow$ q .

5. I will study for the final otherwise I will fail.
Solution: Let p = I will 

study for the final, 
and let q = I will fail.
Then $\neg$p $\rightarrow$ q . \\[\baselineskip]
Problem 2.

1. p $\land$ q and p $\lor$ $\neg$q 

\begin{displaymath}
\begin{array}{|c c|c|c|}
p & q & p \land q & p \lor \neg q\\
\hline
T & T & T & T\\
T & F & F & T\\
F & T & F & F\\
F & F & F & T\\
\end{array}
\end{displaymath}

As we can see, for 2 of the 4 possible cases, these two expressions 

have different outcomes. Therefore, they are not equivalent.

2. p $\lor$ q and $\neg$p $\lor$ $\neg$q 


\begin{displaymath}
\begin{array}{|c c|c|c|}
p & q & p \lor q & \neg p \lor \neg q\\
\hline
T & T & T & F\\
T & F & T & T\\
F & T & T & T\\
F & F & F & T\\
\end{array}
\end{displaymath}

As we can see, for 2 of the 4 possible cases, these two expressions 

have different outcomes. Therefore, they are not equivalent.

%3. p $\rightarrow$ q  and $\neg$q $\rightarrow$ $\neg$p
%\begin{displaymath}
%\begin{array}{|c c|c|c|c|c|}
%p & q & p \rightarrow q & \neg q & \neg p & \neg q \rightarrow \neg p\\
%\hline
%T & T & T & F & F & T\\
%T & F & F & T & F & F\\
%F & T & T & F & T & T\\
%F & F & T & T & T & T\\
%\end{array}
%\end{displaymath}

%As we can see, for all 4 cases these two expressions have the same results. Therefore, they are equivalent.

%4. p $\rightarrow$ q  and $\neg$p $\lor$ q
\end{document}