---
title: "Worksheet 6"
author: "Veronika Nechaeva"
date: "3/4/2021"
output: html_document
---


Goal: To illustrate how to use R to simulate a coin flip game

Two Players: Byron and Paul. We pay attention to only Byron's earnings
      
Each round the fair coin is tossed.

  * Head: Byron wins $1 from Paul.
  * Tails: Byron gives $1 to Paul.

We want to simulate many games and track:
        
  * Number of Heads during a game.
  * Byron's total at the end of the game.
  * Byron's maximum fortune during a game.


### Initialization ##

```{r}
totalGamesPlayed <- 10000; 

gameLength <- 30;
win <- 1;
loss <- -1;

#Placeholders to Store Results
numTossesWon <- 0*c(1:totalGamesPlayed);
totalWinnings <- 0*c(1:totalGamesPlayed);
maxFortune <- 0*c(1:totalGamesPlayed);
```

### Carry out Experiment

```{r}
for (j in seq(from=1,to=totalGamesPlayed,by=1))
{
  #Play the Game
  gameOutcomes <- sample(c(loss,win), size=gameLength, replace=TRUE)
  
  ## NEED TO CHANGE numTossesWon, totalwinnings, and maxFortune
  
  ## (1) Number of Tosses Byron Won (i.e., how many heads) ##
  numTossesWon[j] <- sum(gameOutcomes==1); 
  
  ## (2) What is Byron's Final Total ##
  totalWinnings[j] <- sum(gameOutcomes); 
  
  ## (3) What is Byron's Maximum Fortune ##
  maxFortune[j] <- max(cumsum(gameOutcomes));  
}

```


### 1. Byron's Number Wins (Heads)

```{r}
minTossesWon <- 0; 
maxTossesWon <- gameLength*(1);

xTossesWon <- c(minTossesWon:maxTossesWon);  
pTossesWon <- 0*c(minTossesWon:maxTossesWon); # PMF of tosses won
cTossesWon <- 0*c(minTossesWon:maxTossesWon); # CDF of tosses won
pTossesWon_2 <- 0*c(minTossesWon:maxTossesWon);

for (j in seq(from=1,to=length(xTossesWon),by=1))
{
  pTossesWon[j] <- sum(numTossesWon==xTossesWon[j])/totalGamesPlayed;
}

for (j in seq(from=1,to=31,by=1))
{
  num <- j-1
  pTossesWon_2[j] <- (factorial(30)/(factorial(num)*factorial(30-num)))*(1/2)^(num) *(1/2)^(30-num);
}

cTossesWon <- cumsum(pTossesWon);

```

### 2. Byron's Total Winnings
```{r}

minTotalWinning <- min(totalWinnings); 
maxTotalWinning <- max(totalWinnings); 

xTotalWin <- c(minTotalWinning:maxTotalWinning);
pTotalWin <- 0*c(minTotalWinning:maxTotalWinning);
cTotalWin <- 0*c(minTotalWinning:maxTotalWinning);

for (j in seq(from=1,to=length(xTotalWin),by=1))
{
  pTotalWin[j] <- sum(totalWinnings==xTotalWin[j])/totalGamesPlayed;
}
cTotalWin <- cumsum(pTotalWin);
```

### 3. Byron's Maximum Fortune 
```{r}
minFortuneVal <- min(maxFortune); 
maxFortuneVal <- max(maxFortune); 

xFortune <- c(minFortuneVal:maxFortuneVal);
pFortune <- 0*c(minFortuneVal:maxFortuneVal);
cFortune <- 0*c(minFortuneVal:maxFortuneVal);

for (j in seq(from=1,to=length(xFortune),by=1))
{
  pFortune[j] <- sum(maxFortune==xFortune[j])/totalGamesPlayed;
}

cFortune <- cumsum(pFortune); 
```


### Visualizations 
```{r}
# (1) Wins 
# PMFs
plotTitle <- paste("Empirical PMF of \ # Wins (Heads) in ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xTossesWon,pTossesWon,xlab="Number of Wins (Heads)", ylab="Empirical Probability",type='b',main=plotTitle)
lines(xTossesWon,pTossesWon_2, col = "green")
points(xTossesWon,pTossesWon_2, col = "green")
```

 **Problem 1. **
 
**A. It seems like the graph is symmetric. **

**B. It is a binomial distribution, which follows the following mass function : P(X=k) = (30_C_k)*(1/2)^(k)*(1-1/2)^(30-k)**

**C. As we can see, the two graphs lie almost on top of each other. That means that the simulation is accurate enough.**

```{r}
## (2) Total Winnings
plotTitle <- paste("Empirical PMF of Total Winnings in  ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xTotalWin,pTotalWin,xlab="Total Winnings", ylab="Empirical Probability",type='b',main=plotTitle)
```

**Problem 2. A. Probability that Byron will break even is 0.14. **

**B.The probability that Byron will have $1 at the end of 30 tosses is 0.**

**C. Not all values are possible. Only even values between 30 and -30 are possible since the number of tosses is even(30)**
**, so an odd outcome of dollars won or lost isnt possible.**


```{r}
## (3) Maximum Fortune
plotTitle <- paste("Empirical PMF of Maximum Fortune in  ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xFortune,pFortune,xlab="Total Winnings", ylab="Empirical Probability",type='b',main=plotTitle)
```

**Problem 3. A.The graph is skewed right.**

**B. $2 is Byron’s average best fortune during a 30-toss game**


### CDFs
```{r}
# (1) Wins
plotTitle <- paste("Empirical CDF of \ # Wins (Heads) in ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xTossesWon,cTossesWon,xlab="Number of Wins (Heads)", ylab="Empirical Probability",type='b',main=plotTitle)

# (2) Total Winnings
plotTitle <- paste("Empirical CDF of Total Winnings in  ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xTotalWin,cTotalWin,xlab="Total Winnings", ylab="Empirical Probability",type='b',main=plotTitle)

# (3) Maximum Fortune
plotTitle <- paste("Empirical CDF of Maximum Fortune in  ", gameLength, " Flips\n","\ # Trials = ", totalGamesPlayed, sep = "");
plot(xFortune,cFortune,xlab="Total Winnings", ylab="Empirical Probability",type='b',main=plotTitle)
```


## **Problem 4**

```{r}
# random loss or win array
randArr <- 0*c(minTossesWon:maxTossesWon);
#cummulatuve array (holds current $ value)
cumArr <- 0*c(minTossesWon:maxTossesWon);
numFlips <- 0*c(minTossesWon:maxTossesWon);
possValues <- 0*c(2)
possValues[1] <- -1
possValues[2] <- 1
for (j in seq(from=1,to=31,by=1))
{
  i <- sample(1:2, 1)
  randArr[j] <- possValues[i];
}
cumArr[1]<-randArr[1]
for (j in seq(from=2,to=31,by=1))
{
  cumArr[j] <- cumArr[j-1] + randArr[j];
}
for (j in seq(from=1,to=31,by=1))
{
  numFlips[j] <- (j-1)
}

plotTitle <- paste("Cummulative Winnings in Dollars ", gameLength, " Flips\n");
plot(numFlips,cumArr,xlab="Number of Flips", ylab="Total Earnings",type='b',main=plotTitle)
```

**I have run this graph multiple times and it looks like Byron will be in lead (have more than $0 earnings) 50% of the time on average. This probability makes sense because the chances of him being in the lead vs him not being in the lead ( P(X>0) vs P(X<=0)) are almost 50/50 ( P(X<=0) is a bit higher than P(X>0) because of the "=").**